Uncovering Distributed System Bugs\\ during Testing (not Production!)

### 2015-08-18 overview.tex
updates in overview

Although a significant amount of research has been conducting during the past few decades on how to test distributed systems,

only a small amount of this research was successful enough to be picked up by industry.

>>>>

Although a significant amount of research has been conducted during the past few decades on how to test distributed systems~\cite{lamport1977proving, lamport1994temporal, schuppan2004efficient, killian2007life, yang2009modist}, it is still not clear how to successfully apply all these promising research techniques in a complex production environment.

Product groups are still using techniques such as unit testing, integration testing and stress testing, which although can catch many bugs, they are not able to catch the most tricky ones.
